Towards Cloud Bursting for Extreme Scale Supercomputers\\ (Unrefereed Workshop Manuscript)

### 2014-07-01 paper/src/paper.tex
Changed directory stractures
added new command to paper.tex, and update on intro
several updates
add author
Added comments in motication section, updated paper.tex for building
change format

\documentclass[JIP,draft]{ipsj}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{verbatim}
\usepackage{supertabular}
\bibliographystyle{ipsjunsrt-e.bst}

\begin{document}
\title{Towards Cloud Bursting for Extreme Scale Supercomputers}

@@

\begin{keyword}
Supercomputer, Cloud, I/O Bursting Buffer Model
\end{keyword}

@@

@@

\bibliography{reference}
\end{document}

>>>>

\documentclass[techreq,english]{ipsj}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{verbatim}
\usepackage{supertabular}
\usepackage{flushend}
\usepackage{latexsym}
\usepackage{colortbl}
\bibliographystyle{ipsjunsrt-e.bst}

\newcommand{\kento}[1]{{\color{blue} [Kento: {\it #1}]}}
\definecolor{darkgray}{gray}{0.7}
\definecolor{lightgray}{gray}{0.9}

\def\Underline{\setbox0\hbox\bgroup\let\\\endUnderline}
\def\endUnderline{\vphantom{y}\egroup\smash{\underline{\box0}}\\}
\def\|{\verb|}
\usepackage[varg]{txfonts}
\makeatletter
\input{ot1txtt.fd}
\makeatother
\setcounter{volume}{22}% vol21=2013
\setcounter{number}{1}
\setcounter{page}{1}
\begin{document}
\title{Towards Cloud Bursting for Extreme Scale Supercomputers\\
   (Unrefereed Workshop Manuscript)}

\affiliate{Titech}{Tokyo Institute of Technology, Japan, Tokyo, Meguro, okayama 2-12-1}
\author{Tianqi Xu}{Titech}
\author{Kento Sato}{Titech}
\author{Satoshi Matsuoka}{Titech}

@@

\begin{keyword}
Supercomputer, Cloud, Burst buffer
\end{keyword}

@@

\input{5-5_related_work}

@@

\bibliography{../bib/reference}
\end{document}
